Out-of-Sample Comparisons of Overfit Models

### 2017-04-21 floats/empirics-oos-ind-pm.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25,128.74) --
	( 69.44,113.58) --
	( 75.62,116.70) --
	( 81.80,101.94) --
	( 87.98,102.92) --
	( 94.16,109.79) --
	(100.34,103.33) --
	(106.52,117.62) --
	(112.70,122.31) --
	(118.88,123.05) --
	(125.06,107.38) --
	(131.24,103.26) --
	(137.42,108.90) --
	(143.60, 81.56) --
	(149.78, 73.07) --
	(155.96, 70.30) --
	(162.14, 68.61) --
	(168.32, 68.52) --
	(174.50, 68.01) --
	(180.68, 66.99) --
	(186.86, 67.19) --
	(193.04, 68.04) --
	(199.22, 65.70) --
	(205.40, 65.82) --
	(211.58, 65.23) --
	(217.76, 65.25) --
	(223.94, 65.20) --
	(230.12, 65.91) --
	(236.30, 65.56) --
	(242.48, 65.28) --
	(248.66, 65.84) --
	(254.84, 65.68) --
	(261.02, 65.76) --
	(267.20, 65.83) --
	(273.38, 65.88) --
	(279.57, 64.78) --
	(285.75, 64.82) --
	(291.93, 64.59) --
	(298.11, 64.52) --
	(304.29, 64.56) --
	(310.47, 64.63) --
	(316.65, 64.48) --
	(322.83, 64.47) --
	(329.01, 64.52) --
	(335.19, 64.47) --
	(341.37, 64.51) --
	(347.55, 64.52) --
	(353.73, 64.57) --
	(359.91, 64.47) --
	(366.09, 64.51) --
	(372.27, 64.63) --
	(378.45, 64.81) --
	(384.63, 65.01);

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {Full model};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25,128.74) --
	( 69.44,113.58) --
	( 75.62,116.70) --
	( 81.80,101.94) --
	( 87.98,102.92) --
	( 94.16,109.79) --
	(100.34,103.33) --
	(106.52,117.62) --
	(112.70,122.31) --
	(118.88,123.05) --
	(125.06,107.38) --
	(131.24,103.26) --
	(137.42,108.90) --
	(143.60, 81.56) --
	(149.78, 73.07) --
	(155.96, 70.30) --
	(162.14, 68.61) --
	(168.32, 68.52) --
	(174.50, 68.01) --
	(180.68, 66.99) --
	(186.86, 67.19) --
	(193.04, 68.04) --
	(199.22, 65.70) --
	(205.40, 65.82) --
	(211.58, 65.23) --
	(217.76, 65.25) --
	(223.94, 65.20) --
	(230.12, 65.91) --
	(236.30, 65.56) --
	(242.48, 65.28) --
	(248.66, 65.84) --
	(254.84, 65.68) --
	(261.02, 65.76) --
	(267.20, 65.83) --
	(273.38, 65.88) --
	(279.57, 64.78) --
	(285.75, 64.82) --
	(291.93, 64.59) --
	(298.11, 64.52) --
	(304.29, 64.56) --
	(310.47, 64.63) --
	(316.65, 64.48) --
	(322.83, 64.47) --
	(329.01, 64.52) --
	(335.19, 64.47) --
	(341.37, 64.51) --
	(347.55, 64.52) --
	(353.73, 64.57) --
	(359.91, 64.47) --
	(366.09, 64.51) --
	(372.27, 64.63) --
	(378.45, 64.81) --
	(384.63, 65.01);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 63.80) -- ( 50.40,119.62);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.75) -- ( 44.40, 77.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 91.71) -- ( 44.40, 91.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,105.66) -- ( 44.40,105.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,119.62) -- ( 44.40,119.62);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.00) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 88.95) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,102.91) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,116.86) {4};
\end{scope}
\end{tikzpicture}

>>>>

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 97.34) --
	( 69.44, 97.88) --
	( 75.62, 98.01) --
	( 81.80, 97.62) --
	( 87.98, 97.87) --
	( 94.16, 98.41) --
	(100.34, 98.76) --
	(106.52, 97.50) --
	(112.70, 97.95) --
	(118.88, 98.43) --
	(125.06, 97.50) --
	(131.24, 97.26) --
	(137.42, 97.93) --
	(143.60, 98.08) --
	(149.78, 98.74) --
	(155.96, 97.99) --
	(162.14, 98.74) --
	(168.32, 99.59) --
	(174.50,100.40) --
	(180.68, 99.28) --
	(186.86,100.08) --
	(193.04,100.89) --
	(199.22, 99.90) --
	(205.40,100.40) --
	(211.58,101.38) --
	(217.76,102.37) --
	(223.94,100.30) --
	(230.12, 94.81) --
	(236.30, 94.33) --
	(242.48, 94.91) --
	(248.66, 94.58) --
	(254.84, 95.42) --
	(261.02, 96.47) --
	(267.20, 97.16) --
	(273.38, 95.89) --
	(279.57, 97.03) --
	(285.75, 98.12) --
	(291.93, 99.14) --
	(298.11, 99.59) --
	(304.29,101.00) --
	(310.47,102.50) --
	(316.65,104.29) --
	(322.83,105.29) --
	(329.01,105.81) --
	(335.19,106.66) --
	(341.37,109.14) --
	(347.55,111.98) --
	(353.73,114.58) --
	(359.91,114.85) --
	(366.09,118.06) --
	(372.27,119.90) --
	(378.45,123.28) --
	(384.63,128.74);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (223.94, 15.60) {Observations used for training sample ($R$)};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 12.00, 96.27) {Benchmark};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 97.34) --
	( 69.44, 97.88) --
	( 75.62, 98.01) --
	( 81.80, 97.62) --
	( 87.98, 97.87) --
	( 94.16, 98.41) --
	(100.34, 98.76) --
	(106.52, 97.50) --
	(112.70, 97.95) --
	(118.88, 98.43) --
	(125.06, 97.50) --
	(131.24, 97.26) --
	(137.42, 97.93) --
	(143.60, 98.08) --
	(149.78, 98.74) --
	(155.96, 97.99) --
	(162.14, 98.74) --
	(168.32, 99.59) --
	(174.50,100.40) --
	(180.68, 99.28) --
	(186.86,100.08) --
	(193.04,100.89) --
	(199.22, 99.90) --
	(205.40,100.40) --
	(211.58,101.38) --
	(217.76,102.37) --
	(223.94,100.30) --
	(230.12, 94.81) --
	(236.30, 94.33) --
	(242.48, 94.91) --
	(248.66, 94.58) --
	(254.84, 95.42) --
	(261.02, 96.47) --
	(267.20, 97.16) --
	(273.38, 95.89) --
	(279.57, 97.03) --
	(285.75, 98.12) --
	(291.93, 99.14) --
	(298.11, 99.59) --
	(304.29,101.00) --
	(310.47,102.50) --
	(316.65,104.29) --
	(322.83,105.29) --
	(329.01,105.81) --
	(335.19,106.66) --
	(341.37,109.14) --
	(347.55,111.98) --
	(353.73,114.58) --
	(359.91,114.85) --
	(366.09,118.06) --
	(372.27,119.90) --
	(378.45,123.28) --
	(384.63,128.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 63.80) -- ( 50.40,122.39);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 75.52) -- ( 44.40, 75.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 87.23) -- ( 44.40, 87.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 98.95) -- ( 44.40, 98.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,110.67) -- ( 44.40,110.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,122.39) -- ( 44.40,122.39);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,119.63) {0.05};
\end{scope}
\end{tikzpicture}

### 2017-04-21 floats/empirics-oos-mse-1b.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 63.80) --
	( 69.44, 79.00) --
	( 75.62, 75.81) --
	( 81.80, 90.65) --
	( 87.98, 89.65) --
	( 94.16, 82.75) --
	(100.34, 89.24) --
	(106.52, 74.79) --
	(112.70, 70.07) --
	(118.88, 69.31) --
	(125.06, 85.04) --
	(131.24, 89.19) --
	(137.42, 83.50) --
	(143.60,111.13) --
	(149.78,119.75) --
	(155.96,122.55) --
	(162.14,124.28) --
	(168.32,124.38) --
	(174.50,124.90) --
	(180.68,125.93) --
	(186.86,125.73) --
	(193.04,124.88) --
	(199.22,127.25) --
	(205.40,127.14) --
	(211.58,127.74) --
	(217.76,127.73) --
	(223.94,127.76) --
	(230.12,126.96) --
	(236.30,127.32) --
	(242.48,127.60) --
	(248.66,127.03) --
	(254.84,127.21) --
	(261.02,127.14) --
	(267.20,127.07) --
	(273.38,127.01) --
	(279.57,128.12) --
	(285.75,128.10) --
	(291.93,128.34) --
	(298.11,128.42) --
	(304.29,128.39) --
	(310.47,128.33) --
	(316.65,128.52) --
	(322.83,128.54) --
	(329.01,128.49) --
	(335.19,128.54) --
	(341.37,128.53) --
	(347.55,128.56) --
	(353.73,128.53) --
	(359.91,128.64) --
	(366.09,128.64) --
	(372.27,128.53) --
	(378.45,128.38) --
	(384.63,128.25);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 65.95) --
	( 69.44, 80.70) --
	( 75.62, 77.67) --
	( 81.80, 92.03) --
	( 87.98, 91.07) --
	( 94.16, 84.40) --
	(100.34, 90.69) --
	(106.52, 76.77) --
	(112.70, 72.21) --
	(118.88, 71.50) --
	(125.06, 86.73) --
	(131.24, 90.74) --
	(137.42, 85.25) --
	(143.60,111.86) --
	(149.78,120.13) --
	(155.96,122.81) --
	(162.14,124.47) --
	(168.32,124.56) --
	(174.50,125.07) --
	(180.68,126.05) --
	(186.86,125.86) --
	(193.04,125.05) --
	(199.22,127.31) --
	(205.40,127.20) --
	(211.58,127.78) --
	(217.76,127.77) --
	(223.94,127.80) --
	(230.12,127.04) --
	(236.30,127.38) --
	(242.48,127.66) --
	(248.66,127.11) --
	(254.84,127.28) --
	(261.02,127.21) --
	(267.20,127.15) --
	(273.38,127.09) --
	(279.57,128.17) --
	(285.75,128.14) --
	(291.93,128.38) --
	(298.11,128.46) --
	(304.29,128.43) --
	(310.47,128.38) --
	(316.65,128.55) --
	(322.83,128.57) --
	(329.01,128.53) --
	(335.19,128.58) --
	(341.37,128.57) --
	(347.55,128.60) --
	(353.73,128.58) --
	(359.91,128.68) --
	(366.09,128.68) --
	(372.27,128.58) --
	(378.45,128.44) --
	(384.63,128.32);

@@

@@

\path[fill=fillColor] ( 63.25,128.74) --
	( 63.25, 63.80) --
	( 69.44, 79.00) --
	( 75.62, 75.81) --
	( 81.80, 90.65) --
	( 87.98, 89.65) --
	( 94.16, 82.75) --
	(100.34, 89.24) --
	(106.52, 74.79) --
	(112.70, 70.07) --
	(118.88, 69.31) --
	(125.06, 85.04) --
	(131.24, 89.19) --
	(137.42, 83.50) --
	(143.60,111.13) --
	(149.78,119.75) --
	(155.96,122.55) --
	(162.14,124.28) --
	(168.32,124.38) --
	(174.50,124.90) --
	(180.68,125.93) --
	(186.86,125.73) --
	(193.04,124.88) --
	(199.22,127.25) --
	(205.40,127.14) --
	(211.58,127.74) --
	(217.76,127.73) --
	(223.94,127.76) --
	(230.12,126.96) --
	(236.30,127.32) --
	(242.48,127.60) --
	(248.66,127.03) --
	(254.84,127.21) --
	(261.02,127.14) --
	(267.20,127.07) --
	(273.38,127.01) --
	(279.57,128.12) --
	(285.75,128.10) --
	(291.93,128.34) --
	(298.11,128.42) --
	(304.29,128.39) --
	(310.47,128.33) --
	(316.65,128.52) --
	(322.83,128.54) --
	(329.01,128.49) --
	(335.19,128.54) --
	(341.37,128.53) --
	(347.55,128.56) --
	(353.73,128.53) --
	(359.91,128.64) --
	(366.09,128.64) --
	(372.27,128.53) --
	(378.45,128.38) --
	(384.63,128.25) --
	(384.63,128.74) --
	cycle;
\definecolor[named]{drawColor}{rgb}{0.75,0.75,0.75}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 65.95) --
	( 69.44, 80.70) --
	( 75.62, 77.67) --
	( 81.80, 92.03) --
	( 87.98, 91.07) --
	( 94.16, 84.40) --
	(100.34, 90.69) --
	(106.52, 76.77) --
	(112.70, 72.21) --
	(118.88, 71.50) --
	(125.06, 86.73) --
	(131.24, 90.74) --
	(137.42, 85.25) --
	(143.60,111.86) --
	(149.78,120.13) --
	(155.96,122.81) --
	(162.14,124.47) --
	(168.32,124.56) --
	(174.50,125.07) --
	(180.68,126.05) --
	(186.86,125.86) --
	(193.04,125.05) --
	(199.22,127.31) --
	(205.40,127.20) --
	(211.58,127.78) --
	(217.76,127.77) --
	(223.94,127.80) --
	(230.12,127.04) --
	(236.30,127.38) --
	(242.48,127.66) --
	(248.66,127.11) --
	(254.84,127.28) --
	(261.02,127.21) --
	(267.20,127.15) --
	(273.38,127.09) --
	(279.57,128.17) --
	(285.75,128.14) --
	(291.93,128.38) --
	(298.11,128.46) --
	(304.29,128.43) --
	(310.47,128.38) --
	(316.65,128.55) --
	(322.83,128.57) --
	(329.01,128.53) --
	(335.19,128.58) --
	(341.37,128.57) --
	(347.55,128.60) --
	(353.73,128.58) --
	(359.91,128.68) --
	(366.09,128.68) --
	(372.27,128.58) --
	(378.45,128.44) --
	(384.63,128.32);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.43) -- ( 50.40,128.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.43) -- ( 44.40, 74.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 88.01) -- ( 44.40, 88.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,101.59) -- ( 44.40,101.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,115.16) -- ( 44.40,115.16);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 71.68) {-4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 98.83) {-2};

>>>>

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 64.79) --
	(254.84, 71.45) --
	(261.02, 68.74) --
	(267.20, 66.28) --
	(273.38, 63.80) --
	(279.57,105.64) --
	(285.75,104.73) --
	(291.93,113.66) --
	(298.11,116.70) --
	(304.29,115.54) --
	(310.47,113.47) --
	(316.65,120.29) --
	(322.83,121.13) --
	(329.01,119.16) --
	(335.19,121.19) --
	(341.37,120.79) --
	(347.55,121.75) --
	(353.73,120.97) --
	(359.91,125.03) --
	(366.09,124.93) --
	(372.27,120.92) --
	(378.45,115.37) --
	(384.63,110.14);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 67.69) --
	(254.84, 74.06) --
	(261.02, 71.45) --
	(267.20, 69.09) --
	(273.38, 66.79) --
	(279.57,107.26) --
	(285.75,106.40) --
	(291.93,115.08) --
	(298.11,118.01) --
	(304.29,116.97) --
	(310.47,115.08) --
	(316.65,121.60) --
	(322.83,122.36) --
	(329.01,120.66) --
	(335.19,122.70) --
	(341.37,122.44) --
	(347.55,123.48) --
	(353.73,122.73) --
	(359.91,126.40) --
	(366.09,126.32) --
	(372.27,122.61) --
	(378.45,117.59) --
	(384.63,112.83);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (223.94, 15.60) {Observations used for training sample ($R$)};

@@

\path[fill=fillColor] (248.66,128.74) --
	(248.66, 64.79) --
	(254.84, 71.45) --
	(261.02, 68.74) --
	(267.20, 66.28) --
	(273.38, 63.80) --
	(279.57,105.64) --
	(285.75,104.73) --
	(291.93,113.66) --
	(298.11,116.70) --
	(304.29,115.54) --
	(310.47,113.47) --
	(316.65,120.29) --
	(322.83,121.13) --
	(329.01,119.16) --
	(335.19,121.19) --
	(341.37,120.79) --
	(347.55,121.75) --
	(353.73,120.97) --
	(359.91,125.03) --
	(366.09,124.93) --
	(372.27,120.92) --
	(378.45,115.37) --
	(384.63,110.14) --
	(384.63,128.74) --
	cycle;
\definecolor[named]{drawColor}{rgb}{0.75,0.75,0.75}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 67.69) --
	(254.84, 74.06) --
	(261.02, 71.45) --
	(267.20, 69.09) --
	(273.38, 66.79) --
	(279.57,107.26) --
	(285.75,106.40) --
	(291.93,115.08) --
	(298.11,118.01) --
	(304.29,116.97) --
	(310.47,115.08) --
	(316.65,121.60) --
	(322.83,122.36) --
	(329.01,120.66) --
	(335.19,122.70) --
	(341.37,122.44) --
	(347.55,123.48) --
	(353.73,122.73) --
	(359.91,126.40) --
	(366.09,126.32) --
	(372.27,122.61) --
	(378.45,117.59) --
	(384.63,112.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 50.40,128.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 44.40, 77.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 90.65) -- ( 44.40, 90.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,103.34) -- ( 44.40,103.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,116.04) -- ( 44.40,116.04);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.19) {-.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,100.59) {-0.5};

### 2017-04-21 floats/empirics-oos-mse-2.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 64.79) --
	(254.84, 71.45) --
	(261.02, 68.74) --
	(267.20, 66.28) --
	(273.38, 63.80) --
	(279.57,105.64) --
	(285.75,104.73) --
	(291.93,113.66) --
	(298.11,116.70) --
	(304.29,115.54) --
	(310.47,113.47) --
	(316.65,120.29) --
	(322.83,121.13) --
	(329.01,119.16) --
	(335.19,121.19) --
	(341.37,120.79) --
	(347.55,121.75) --
	(353.73,120.97) --
	(359.91,125.03) --
	(366.09,124.93) --
	(372.27,120.92) --
	(378.45,115.37) --
	(384.63,110.14);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 67.69) --
	(254.84, 74.06) --
	(261.02, 71.45) --
	(267.20, 69.09) --
	(273.38, 66.79) --
	(279.57,107.26) --
	(285.75,106.40) --
	(291.93,115.08) --
	(298.11,118.01) --
	(304.29,116.97) --
	(310.47,115.08) --
	(316.65,121.60) --
	(322.83,122.36) --
	(329.01,120.66) --
	(335.19,122.70) --
	(341.37,122.44) --
	(347.55,123.48) --
	(353.73,122.73) --
	(359.91,126.40) --
	(366.09,126.32) --
	(372.27,122.61) --
	(378.45,117.59) --
	(384.63,112.83);

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (223.94, 15.60) {Observations used for training sample ($R$)};

@@

\path[fill=fillColor] (248.66,128.74) --
	(248.66, 64.79) --
	(254.84, 71.45) --
	(261.02, 68.74) --
	(267.20, 66.28) --
	(273.38, 63.80) --
	(279.57,105.64) --
	(285.75,104.73) --
	(291.93,113.66) --
	(298.11,116.70) --
	(304.29,115.54) --
	(310.47,113.47) --
	(316.65,120.29) --
	(322.83,121.13) --
	(329.01,119.16) --
	(335.19,121.19) --
	(341.37,120.79) --
	(347.55,121.75) --
	(353.73,120.97) --
	(359.91,125.03) --
	(366.09,124.93) --
	(372.27,120.92) --
	(378.45,115.37) --
	(384.63,110.14) --
	(384.63,128.74) --
	cycle;
\definecolor[named]{drawColor}{rgb}{0.75,0.75,0.75}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 67.69) --
	(254.84, 74.06) --
	(261.02, 71.45) --
	(267.20, 69.09) --
	(273.38, 66.79) --
	(279.57,107.26) --
	(285.75,106.40) --
	(291.93,115.08) --
	(298.11,118.01) --
	(304.29,116.97) --
	(310.47,115.08) --
	(316.65,121.60) --
	(322.83,122.36) --
	(329.01,120.66) --
	(335.19,122.70) --
	(341.37,122.44) --
	(347.55,123.48) --
	(353.73,122.73) --
	(359.91,126.40) --
	(366.09,126.32) --
	(372.27,122.61) --
	(378.45,117.59) --
	(384.63,112.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 50.40,128.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 44.40, 77.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 90.65) -- ( 44.40, 90.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,103.34) -- ( 44.40,103.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,116.04) -- ( 44.40,116.04);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.19) {-.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,100.59) {-0.5};

>>>>

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 63.80) --
	( 69.44, 79.00) --
	( 75.62, 75.65) --
	( 81.80, 90.54) --
	( 87.98, 89.54) --
	( 94.16, 82.61) --
	(100.34, 89.12) --
	(106.52, 74.63) --
	(112.70, 69.89) --
	(118.88, 69.13) --
	(125.06, 84.91) --
	(131.24, 89.07) --
	(137.42, 83.37) --
	(143.60,111.11) --
	(149.78,119.79) --
	(155.96,122.58) --
	(162.14,124.34) --
	(168.32,124.44) --
	(174.50,124.99) --
	(180.68,126.15) --
	(186.86,125.94) --
	(193.04,125.01) --
	(199.22,127.58) --
	(205.40,127.46) --
	(211.58,128.46) --
	(217.76,128.40) --
	(223.94,128.54) --
	(230.12,128.70) --
	(236.30,128.70) --
	(242.48,128.68) --
	(248.66,128.71) --
	(254.84,128.72) --
	(261.02,128.72) --
	(267.20,128.71) --
	(273.38,128.71) --
	(279.57,128.69) --
	(285.75,128.71) --
	(291.93,128.71) --
	(298.11,128.71) --
	(304.29,128.70) --
	(310.47,128.70) --
	(316.65,128.70) --
	(322.83,128.69) --
	(329.01,128.70) --
	(335.19,128.71) --
	(341.37,128.71) --
	(347.55,128.71) --
	(353.73,128.70) --
	(359.91,128.70) --
	(366.09,128.68) --
	(372.27,128.59) --
	(378.45,128.44) --
	(384.63,128.30);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] ( 63.25, 65.95) --
	( 69.44, 80.71) --
	( 75.62, 77.52) --
	( 81.80, 91.92) --
	( 87.98, 90.96) --
	( 94.16, 84.27) --
	(100.34, 90.58) --
	(106.52, 76.61) --
	(112.70, 72.04) --
	(118.88, 71.33) --
	(125.06, 86.60) --
	(131.24, 90.62) --
	(137.42, 85.12) --
	(143.60,111.84) --
	(149.78,120.17) --
	(155.96,122.84) --
	(162.14,124.53) --
	(168.32,124.63) --
	(174.50,125.16) --
	(180.68,126.27) --
	(186.86,126.07) --
	(193.04,125.19) --
	(199.22,127.64) --
	(205.40,127.53) --
	(211.58,128.47) --
	(217.76,128.42) --
	(223.94,128.55) --
	(230.12,128.71) --
	(236.30,128.71) --
	(242.48,128.68) --
	(248.66,128.72) --
	(254.84,128.73) --
	(261.02,128.72) --
	(267.20,128.72) --
	(273.38,128.71) --
	(279.57,128.70) --
	(285.75,128.72) --
	(291.93,128.72) --
	(298.11,128.72) --
	(304.29,128.72) --
	(310.47,128.71) --
	(316.65,128.72) --
	(322.83,128.70) --
	(329.01,128.71) --
	(335.19,128.72) --
	(341.37,128.72) --
	(347.55,128.72) --
	(353.73,128.72) --
	(359.91,128.72) --
	(366.09,128.71) --
	(372.27,128.62) --
	(378.45,128.49) --
	(384.63,128.37);

@@

@@

\path[fill=fillColor] ( 63.25,128.74) --
	( 63.25, 63.80) --
	( 69.44, 79.00) --
	( 75.62, 75.65) --
	( 81.80, 90.54) --
	( 87.98, 89.54) --
	( 94.16, 82.61) --
	(100.34, 89.12) --
	(106.52, 74.63) --
	(112.70, 69.89) --
	(118.88, 69.13) --
	(125.06, 84.91) --
	(131.24, 89.07) --
	(137.42, 83.37) --
	(143.60,111.11) --
	(149.78,119.79) --
	(155.96,122.58) --
	(162.14,124.34) --
	(168.32,124.44) --
	(174.50,124.99) --
	(180.68,126.15) --
	(186.86,125.94) --
	(193.04,125.01) --
	(199.22,127.58) --
	(205.40,127.46) --
	(211.58,128.46) --
	(217.76,128.40) --
	(223.94,128.54) --
	(230.12,128.70) --
	(236.30,128.70) --
	(242.48,128.68) --
	(248.66,128.71) --
	(254.84,128.72) --
	(261.02,128.72) --
	(267.20,128.71) --
	(273.38,128.71) --
	(279.57,128.69) --
	(285.75,128.71) --
	(291.93,128.71) --
	(298.11,128.71) --
	(304.29,128.70) --
	(310.47,128.70) --
	(316.65,128.70) --
	(322.83,128.69) --
	(329.01,128.70) --
	(335.19,128.71) --
	(341.37,128.71) --
	(347.55,128.71) --
	(353.73,128.70) --
	(359.91,128.70) --
	(366.09,128.68) --
	(372.27,128.59) --
	(378.45,128.44) --
	(384.63,128.30) --
	(384.63,128.74) --
	cycle;
\definecolor[named]{drawColor}{rgb}{0.75,0.75,0.75}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25, 65.95) --
	( 69.44, 80.71) --
	( 75.62, 77.52) --
	( 81.80, 91.92) --
	( 87.98, 90.96) --
	( 94.16, 84.27) --
	(100.34, 90.58) --
	(106.52, 76.61) --
	(112.70, 72.04) --
	(118.88, 71.33) --
	(125.06, 86.60) --
	(131.24, 90.62) --
	(137.42, 85.12) --
	(143.60,111.84) --
	(149.78,120.17) --
	(155.96,122.84) --
	(162.14,124.53) --
	(168.32,124.63) --
	(174.50,125.16) --
	(180.68,126.27) --
	(186.86,126.07) --
	(193.04,125.19) --
	(199.22,127.64) --
	(205.40,127.53) --
	(211.58,128.47) --
	(217.76,128.42) --
	(223.94,128.55) --
	(230.12,128.71) --
	(236.30,128.71) --
	(242.48,128.68) --
	(248.66,128.72) --
	(254.84,128.73) --
	(261.02,128.72) --
	(267.20,128.72) --
	(273.38,128.71) --
	(279.57,128.70) --
	(285.75,128.72) --
	(291.93,128.72) --
	(298.11,128.72) --
	(304.29,128.72) --
	(310.47,128.71) --
	(316.65,128.72) --
	(322.83,128.70) --
	(329.01,128.71) --
	(335.19,128.72) --
	(341.37,128.72) --
	(347.55,128.72) --
	(353.73,128.72) --
	(359.91,128.72) --
	(366.09,128.71) --
	(372.27,128.62) --
	(378.45,128.49) --
	(384.63,128.37);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.27) -- ( 50.40,128.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 74.27) -- ( 44.40, 74.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 87.89) -- ( 44.40, 87.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,101.51) -- ( 44.40,101.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,115.12) -- ( 44.40,115.12);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 71.51) {-4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 98.75) {-2};
